curacao_threeplayers_rest_monster

### 2020-09-29 inst/curacao1962_threeplayers_rest_monster.Rmd
clarification of monster's status

  if(white_player_rested){  
    if(       result == "1-0"){ 
      I[c(white_player,             "white","rest"            )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else if(black_player_rested){
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player,        "rest"            )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else { # neither player rested
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white",       drawmonster)] %<>% dec
  }
}

>>>>

  if(white_player_rested){  
    if(       result == "1-0"){ 
      I[c(white_player,             "white","rest"            )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else if(black_player_rested){
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player,        "rest"            )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white","rest",drawmonster)] %<>% dec
  } else { # neither player rested, rest monster inactive
    if(       result == "1-0"){ 
      I[c(white_player,             "white"                   )] %<>% inc
    } else if(result == "0-1"){ 
      I[c(             black_player                           )] %<>% inc
    } else if(result == "1/2-1/2"){                         
      I[c(                                         drawmonster)] %<>% inc
    } else { prob() }
      I[c(white_player,black_player,"white",       drawmonster)] %<>% dec
  }
}
